%! Author = sujal
%! Date = 3/18/23

% Preamble
\documentclass[11pt]{article}
\pagenumbering{gobble}

% Packages
\usepackage{amsmath}
\usepackage[letterpaper, margin=0.8in, top=0.9in]{geometry}
\usepackage[
    pdftitle={Sujal Singh - Resume},
    pdfsubject={Resume},
    pdfauthor={Sujal Singh},
    pdfdisplaydoctitle,
    hidelinks,
]{hyperref}
\usepackage{tabularx}
\usepackage{array}
\usepackage{multirow}
\usepackage{lettrine}
\usepackage{color}
\usepackage{fontawesome5}
\usepackage{etoolbox}

%% Fonts
\usepackage[T1]{fontenc}
\usepackage{lmodern}

% Variables
\newtoggle{lines}
\togglefalse{lines}


% Document
\begin{document}
    % -------------------------------------------------- Title -------------------------------------------------- %
    \noindent
    \begin{tabularx}{\textwidth}{l X l}
        \hspace{-4px}
        \href{https://github.com/sujaldev}{\faGithub} \hspace{0px}
        \href{https://youtube.com/@sujaldev}{\faYoutube} \hspace{0px}
        \href{https://gitlab.com/sujaldev}{\faGitlab} \hspace{0px}
        \href{https://stackexchange.com/users/20453278/sujal?tab=accounts}{\faStackExchange} \hspace{0px}
        \href{https://stackoverflow.com/users/15007549/sujal-singh}{\faStackOverflow} \hspace{0px}
        \\
        \href{mailto:contact@sujal.dev}{\texttt{contact@sujal.dev}} & &
        \multirow{2}{*}[2ex]{\href{https://sujal.dev}{\textbf{\Huge Sujal Singh}}} \\ \\
    \end{tabularx} \\ \\
    % ----------------------------------------------------------------------------------------------------------- %


    % -------------------------------------------------- Info --------------------------------------------------- %
    \noindent
    \begin{tabularx}{\textwidth}{@{}b{90px} b{9px}@{} X@{}}
        % ---------------------------------------------- Experience --------------------------------------------- %
        \iftoggle{lines}{\\ \\ \hline \\}{}

        \lettrine[lines=1,loversize=-0.5]{P}ROJECTS & $\diamond$ &

        \textbf{Computer Graphics} \hfill \\ & &
        \vspace{-13pt}
        \begin{itemize}
            \item \href{https://github.com/sujaldev/skylon}{\color{blue}Skylon} is a web browser rendering engine
            written entirely from scratch which implements an HTML parser, a CSS parser and a rendering pipeline.
            \item \href{https://github.com/sujaldev/lyn}{\color{blue}Lyn} is a tiny programming language built at a
            24-hour hackathon that compiles input code into visual animations.
        \end{itemize}

        \\ & $\diamond$ &

        \textbf{Computer Networking} \\ & &
        \vspace{-13pt}
        \begin{itemize}
            \item \textbf{Delhi Police -- Cybersecurity Hackathon}\hfill\textit{February 2024}\newline
            Secured first position and a reward of 12k INR for developing a filter that actively prevents any client
            device from accessing potentially malicious URLs. For proxying traffic, the wireguard mode in mitmproxy
            was used and filtering logic is injected via a mitmproxy addon.
            \href{https://github.com/sujaldev/cerberus}{\color{blue}Source Code}
            \item \textbf{ACT Fibernet}\hfill\textit{March 2023}\newline
            Rewarded 10k INR for reporting a severe flaw in the implementation of the ISP's intranet firewall rules,
            with another two reports that are currently under review.
            \href{https://pdf.sujal.dev/act/report.pdf}{\color{blue} Read report}
        \end{itemize}

        \\ & $\diamond$ &

        \textbf{3D Printer} \hfill \textit{July 2019} \\ & &
        Won second prize in a science fair for building a 3D printer.\ Currently migrating this printer to a core-xy
        motion system for which I'm designing the parts from scratch for fun.
        \href{https://github.com/xserv-labs/cad}{\color{blue}Source Repository}.

        \\ & $\diamond$ &

        \textbf{Home Server} \hfill \textit{July 2019} \\ & &
        My sibling and I maintain several home servers: a firewall, two virtualization nodes running proxmox which
        serve various purposes including network storage, media management, 3D printer firmware and more, and a
        Raspberry Pi running KVM over IP for remote management.
        \href{https://github.com/xserv-labs}{\color{blue}Related Repositories}.\

        \iftoggle{lines}{\\ \\ \hline \\}{\\ \\}
        % ------------------------------------------------------------------------------------------------------- %


        % ------------------------------------------------ Skills ----------------------------------------------- %
        \lettrine[lines=1,loversize=-0.5]{S}KILLS & $\diamond$ &

        \textbf{Languages:} Python, HTML/CSS, JavaScript, \LaTeX, Bash, Lyn & &

        \\ & $\diamond$ &

        \textbf{Others:} Git, GitHub, Linux \\ & &

        \iftoggle{lines}{\\ \\ \hline \\}{\\ \\}
        % ------------------------------------------------------------------------------------------------------- %


        % ----------------------------------------------- Education --------------------------------------------- %
        \lettrine[lines=1,loversize=-0.5]{E}DUCATION & $\diamond$ &

        \textbf{University School of Automation \& Robotics} \hfill \textit{September 2023 -- 2027} \\ & &
        Bachelor of Technology in Industrial Internet of Things.

        \\ & $\diamond$ &

        \textbf{St. Xavier's School, Rohini} \hfill \textit{March 2010 -- June 2022} \\ & &
        Studied Physics, Chemistry, Mathematics, Computer Science and English.

        \iftoggle{lines}{\\ \\ \hline \\}{\\ \\}
        % ------------------------------------------------------------------------------------------------------- %

    \end{tabularx}
    % ----------------------------------------------------------------------------------------------------------- %


\end{document}