%! Author = Sujal Singh
%! Date = 3/18/23

% Preamble
\documentclass[11pt]{article}

% Packages
\usepackage{amsmath}
\usepackage[letterpaper,margin=3cm]{geometry}
\usepackage[
    pdftitle={Sujal Singh - Resume},
    pdfsubject={Resume},
    pdfauthor={Sujal Singh},
    pdfdisplaydoctitle,
    hidelinks,
]{hyperref}
\usepackage{tabularray}
\usepackage{color}
\usepackage{fontawesome5}
\usepackage{enumitem}

%% Fonts
\usepackage[T1]{fontenc}
\usepackage{lmodern}

\pagenumbering{gobble}
\UseTblrLibrary{varwidth}
\renewcommand{\labelitemi}{\diamond}
\renewcommand{\labelitemii}{\textbullet}

% Document
\begin{document}
    \noindent%
    \begin{tblr}%
    {colspec={X[3,l,t]X[11,l,t]},colsep=0pt,rowsep=10pt,row{1-4}={rowsep=0pt},cell{1}{2}={r=2,c=1}{r,f},measure=vbox}%
        % ------------------------------------------------------------------------------------------------------------ %
        % -------------------------------------------------- Title --------------------------------------------------- %
        % ------------------------------------------------------------------------------------------------------------ %
        \href{https://github.com/sujaldev}{\faGithub}
        \hspace{5pt} \href{https://linkedin.com/in/sujal-singh}{\faLinkedin}
        \hspace{5pt} \href{https://youtube.com/@sujaldev}{\faYoutube}
        &
        \href{https://sujal.dev/}{\textbf{\Huge Sujal Singh}}
        \\
        \href{mailto:contact@sujal.dev}{\texttt{contact@sujal.dev}}
        \\ \\
        % ------------------------------------------------------------------------------------------------------------ %
        % ------------------------------------------------ Projects -------------------------------------------------- %
        % ------------------------------------------------------------------------------------------------------------ %
        \textsc{\Large Projects} &
        \vspace*{-1.5\topsep}
        \begin{itemize}[topsep=0pt,leftmargin=15pt]
            \item \textbf{Computer Graphics}
            \begin{itemize}
                \item \href{https://github.com/sujaldev/skylon}{\color{blue}Skylon} is a web browser rendering engine
                written entirely from scratch which implements an HTML parser, a CSS parser and a rendering pipeline.
                \item \href{https://github.com/sujaldev/lyn}{\color{blue}Lyn} is a tiny programming language built at a
                24-hour hackathon that compiles input code into visual animations.
            \end{itemize}

            % -------------------------------------------------------------------------------------------------------- %

            \item \textbf{Computer Networking}
            \begin{itemize}
                \item \textbf{Delhi Police -- Cybersecurity Hackathon}\hfill\textit{February 2024}\newline
                Secured first position and a reward of 12k INR for developing a filter that actively prevents any client
                device from accessing potentially malicious URLs. For proxying traffic, the wireguard mode in mitmproxy
                was used and filtering logic is injected via a mitmproxy addon.
                \href{https://github.com/sujaldev/cerberus}{\color{blue}Source Code}
                \item \textbf{ACT Fibernet}\hfill\textit{March 2023}\newline
                Rewarded 10k INR for reporting a severe flaw in the implementation of the ISP's intranet firewall rules,
                with another two reports that are currently a draft.
                \href{https://pdf.sujal.dev/act/report.pdf}{\color{blue} Read report}
            \end{itemize}

            % -------------------------------------------------------------------------------------------------------- %

            \item \textbf{3D Printer}\\
            Won second prize in a science fair for building a 3D printer.\ Currently migrating this printer to a core-xy
            motion system for which I'm designing the parts from scratch for fun.
            \href{https://github.com/xserv-labs/cad}{\color{blue}Source Repository}.

            % -------------------------------------------------------------------------------------------------------- %

            \item \textbf{Home Server}\\
            My sibling and I maintain several home servers: a firewall, two virtualization nodes running proxmox which
            serve various purposes including network storage, media management, 3D printer firmware and more, and a
            Raspberry Pi running KVM over IP for remote management.
            \href{https://github.com/xserv-labs}{\color{blue}Related Repositories}.\
        \end{itemize}
        \\
        % ------------------------------------------------------------------------------------------------------------ %
        % ------------------------------------------------- Skills --------------------------------------------------- %
        % ------------------------------------------------------------------------------------------------------------ %
        \textsc{\Large Skills} &
        \vspace*{-1.5\topsep}
        \begin{itemize}[topsep=0pt,leftmargin=15pt]
            \item \textbf{Languages:} Proficient in Python.\ Familiar with \LaTeX, HTML/CSS, JavaScript, Bash, OpenSCAD.
            \item \textbf{Others:} Git, Docker, Linux Administration, Autodesk Fusion.
        \end{itemize}
        \\
        % ------------------------------------------------------------------------------------------------------------ %
        % ----------------------------------------------- Education -------------------------------------------------- %
        % ------------------------------------------------------------------------------------------------------------ %
        \textsc{\Large Education} &
        \vspace*{-1.5\topsep}
        \begin{itemize}[topsep=0pt,leftmargin=15pt]
            \item \textbf{University School of Automation \& Robotics} \hfill \textit{2023~--~2027} \\
            Bachelor of Technology in Industrial Internet of Things. \hfill GPA: 7.4
            \item \textbf{St. Xavier's School, Rohini} \hfill \textit{2010~--~2022} \\
            Central Board of Secondary Education \hfill Percentage: $82\%$
        \end{itemize}
    \end{tblr}
\end{document}
